Analysis

### 2017-03-23 Analysis.Rmd
Clean up output in Analysis.Rmd/md and add resources to main README.md

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2015 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2015,
                      REML = FALSE)
summary(TShB_lmm_2015)

@@

## Leaf Sheath Blight Severity Model
```{r}
LShB_lmm_2016 <- lmer(LShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(LShB_lmm_2016)

@@

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2016 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(TShB_lmm_2016)

>>>>

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2015 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2015,
                      REML = FALSE)
summary(TShB_lmm_2015, correlation = FALSE)

@@

## Leaf Sheath Blight Severity Model
```{r}
LShB_lmm_2016 <- lmer(LShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(LShB_lmm_2016, correlation = FALSE)

@@

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2016 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(TShB_lmm_2016, correlation = FALSE)
